%!TEX root = ../_preamble.tex
\begin{acknowledgements}
\textit{Thank you to the many people who made this work possible.}

\textit{I would like to thank my parents for tolerating me for so many years, I've finally found a way to take all the angst and DMCA shutoffs and bricked computers and go pro.}

\textit{Thank you to my lab for supporting me through this project, my advisor Mike Wehr, Lucas Ott who keeps everything running, Nick Sattler, Sam Mehan, Molly Shallows, Alexa Wright, Tillie Morris, Rocky Penick, and Matt Nardoci. Thank you to my dissertation committee, Melissa Baese-Berk, Santiago Jaramillo, and Matt Smear for making sure I stay within the bounds of reason. I would be writing this having been summarily kicked out of academia without the help of Lori Olsen, who shielded and guided me through the viscera of the institution. She is a true testament to how science would simply grind to a halt without those who organize the work.}

\textit{My view on the world has been profoundly shaped by the Janet Smith House and all of the people that I have had the blessing of living with here. There is nothing that has given me hope for the future more than what I have learned in cooperation with you all.}

\textit{Thank you to the many people who were willing to talk with me at length, contributing their wisdom and perspective on the many fields that I would have otherwise stumbled through. In alphabetical order to avoid the appearance of hierarchy: Joon An, Andrey Andreev, Björn Brembs, Nire Bryce, Joel Chan, Kris Chauvin, Jeremy Delahanty, Avery Everhart, Dan Goodman, Olivia Guest, Eartha Mae Guthman, Leslie Harka, Gabriele Hayden, Ceci Herbert, Andrew Hoffman, Os Keyes, Irene Knapp, Mark Laubach \& Open Behavior Team, Christine Lemmer-Webber, Gonçalo Lopes, Mackenzie Mathis, Danny Mclanahan, James Meickle, the NWB \& DANDI teams, Phil Parker, Ralph Emilio Peterson, Tomasz Pluskiewicz, Chris Rodgers, Manuel Schottdorf, Arnold Schrijver, Sanjay Srivastava \& Metascience Class, Petar Todorov, Aad Versteden, Lauren E. Wool, and The Emerging ONICE team. If we talked and I have left you off this list, please let me know, as credit is at the heart of this work.}

\textit{Thank you to my dear Rumbly Tumbly Lawnmower for being the light of my life.}

\end{acknowledgements}